Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-12 tex/VHzQ.tex
SDSSJ0959+0227LC_20190612.png now in .tex
VHzQ update

\begin{figure}
    \centering
    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
  \vspace{-14pt}
    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
      (grey colour-scale). }
    \label{fig:W1W2W3}
\end{figure}
\subsection{MIR Colours}
Due to the depth all-sky coverage of the WISE (and NEOWISE-(R)) mission, 
several investigations have looked at how WISE detects AGN 
\citet[e.g][]{Secrest2015, Assef2015, Stern2015, Assef2018, LaMassa2017, Glikman2018, LaMassa2019}

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm]
  {../light_curves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
  \vspace{-16pt}
  \caption[]
  {Histogram showing the total number of exposures for each detected VH$z$Q
    from the full combination of ALLWISE, NEOWISE and NEOWISE-R.} 
  \label{fig:MIR_LC_epochs}
\end{figure}
\subsection{Variability}
VH$z$Qs, if accreting at, or above the Eddington Limit, might well have have large values of changing mass accretion rate, $\ddot{m}_{\rm accr}$. A consequence of this would be that these quasars exhibit signs of variability, most likely showing up in their UV/optical rest-frame spectra. We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs.

@@

Using the extended datasets described in Section~\ref{sec:NIR_data}, 
we select objects with at least 8
measurements observed with durations over 30 days, in at least one
filter and with the average calibrated flux is greater than 0 and at
least $8\times$ the error on the average calibrated flux. 
%At least 8 original observations across at least 30 days in either WSA or VSA per 
% band, calibrated flux greater than zero over the whole time, and the
% error on the average flux is 8 times lower than this. 
A requirement of SNR$>3$ per `average' epoch, where `average epoch' is
then dependent on the averaging timescales (which as we see can vary).
The clipped median and standard deviation is then calculated 
\begin{equation}
     1.48 \times \sigma_{median} / \bar{\epsilon}
\end{equation}
where $\bar{\epsilon}$ is the mean of the error in each point in the
light curve, divided by the total number of points.
%%
With this definition, although some of the objects have very well sampled 
with an ``average'' light curve sampling over e.g. a month, or two weeks. 
%%
With these criteria, there are 21 WFCAM and 12 VISTA objects 
with 1 object (VIK J1148+0056 ) in common to both, and this sample of 32 is our starting point for variability investigations.

@@

\begin{figure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
    \caption{SHELLQs J0220-0432}
    \label{fig:SHELLQsJ0220-0432}
  \end{subfigure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
    \caption{SDSS J0959+0227}
    \label{fig:SDSSJ0959+0227}
  \end{subfigure}
  \medskip
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
    {../color_color/W1W2_plots/W1W2W3/W1W2W3_hexplots_20190610v2.png} 
  \vspace{-14pt}
    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
      (grey colour-scale). }
    \label{fig:W1W2W3}
\end{figure}
\subsection{MIR Colours}
Due to the depth all-sky coverage of the WISE (and NEOWISE-(R)) mission, 
several investigations have looked at how WISE detects AGN 
\citet[e.g][]{Stern2012, Assef2012, Secrest2015, LaMassa2017, Assef2018, Glikman2018, LaMassa2019}

@@

\begin{figure}
  \centering
  \includegraphics[width=8.5cm]
  {../light_curves/MIR_LCs/NEOWISER_LC_histogramlog_20180827.png}
  \vspace{-16pt}
  \caption[]
  {Histogram showing the total number of exposures for each detected VH$z$Q
    from the full combination of ALLWISE, NEOWISE and NEOWISE-R.} 
  \label{fig:MIR_LC_epochs}
\end{figure}
\subsection{Variability}
VH$z$Qs, if accreting at, or above the Eddington limit, might well have changing mass accretion rates, $\dot{m}_{\rm accr}$. A consequence of this would be that these quasars exhibit signs of variability, most likely showing up in their UV/optical rest-frame emission. We look for evidence of this variability signature in the NIR and MIR light-curves of the VH$z$Qs.

@@

Using the extended datasets described in Section~\ref{sec:NIR_data}, 
we select objects with at least 8 measurements observed with intervals of 
at least 30 days, in at least one filter. 
The signal-to-noise on the average calibrated flux is required to be $\geq8$. 
%(i.e. {\tt aperJky3}$>0$. 
%%(i.e. the average calibrated flux over all epochs must be >0) 
%and 
%{\tt aperJky3/aperJky3Err}$>=$8)
%%
A requirement of SNR$>3$ per `average' epoch, where `average epoch' is
dependent on the averaging timescales is also required.
The clipped median and standard deviation is then calculated 
\begin{equation}
      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
\end{equation}
where $var$ is the index of variation, 
m.a.d. is the median absolute deivation, 
and $\bar{\epsilon}$ is the mean of the error in each point in the
light curve, divided by the total number of points.
%%
With these criteria, there are 21 WFCAM and 12 VISTA objects 
with 1 object (VIK J1148+0056 ) in common to both, and this sample of 32 is our starting point for variability investigations.

@@

\begin{figure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
    \caption{SHELLQs J0220-0432}
    \label{fig:SHELLQsJ0220-0432}
  \end{subfigure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SDSSJ0959+0227LC_20190612.png}
    \caption{SDSS J0959+0227}
    \label{fig:SDSSJ0959+0227}
  \end{subfigure}
  \medskip
\end{figure}
